%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{sébastien}{rey-coyrehourcq}
       {Geomatics engineer}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    14 rue carnot
    94270 Kremlin Bicetre
    France
    ~
    \href{mailto:rey.sebastien@parisgeo.cnrs.fr}{rey.sebastien@\\parisgeo.cnrs.fr}
    %\href{http://friggeri.net}{http://friggeri.net}
    %\href{http://facebook.com/adrien}{fb://adrien}
  \section{languages}
    english notions
  \section{programming}
    Scala
    Python, ObjC
    CSS3 \& HTML5
  \section{GIS software}
    QGIS / ArcGis 9.3
    Postgis
    GeoServer
  \section{CAD}
    Illustrator
    Indesign
    Photoshop
\end{aside}

\section{interests}

complex systems, geography, geomatics, agent-based modelisation, \\spatial data mining, spatial data visualization

\section{education}

\begin{entrylist}
  \entry
    {since 2010}
    {Ph.D. {\normalfont candidate in Geography}}
    {UMR 8054, Geographie-Cités}
    {\emph{A collaborative and modular geomatics platform for urban systems simulations}}
  \entry
    {2008-2009}
    {Md of Geographic Information Systems Engineer}
    {Université Paris 1 - Paris 7 - ENSG}
    {Specialization in Geographic Information Sciences}
  \entry
    {2004–2006}
    {Md. of Computer Science}
    {Université de Pau et des pays de l Adour (UPPA)}
    {Specialization in 3D vizualization}
  \entry
    {2003–2004}
    {Bd. of Computer Science}
    {Université de Pau et des pays de l Adour (UPPA)}
    {Specialization in Web design and Multimedia}
  \entry
    {2001–2003}
    {Ad. of Computer Science}
    {Université de Pau et des pays de l Adour (UPPA)}
    {Specialization in software engineering}
  \entry
    {2001}
    {French Baccalauréat S.}
    {Lycée René Cassin, Bayonne}
    {Specialization in biology}
\end{entrylist}

\section{awards and honor}

R2DS (Réseau de Recherche sur le Développement Soutenable)\\
\emph{Ile-de-France 2010}

\section{experience}

\begin{entrylist}
  \entry
    {05–10 2009}
    {UMR8504 Geographie-Cités/CNRS, Paris}
    {Research Internship.}
    {\emph{Multiple local development on Simpop2 Agent Based Model.}}
  \entry
    {01–02 2009}
    {UMR8504/Geographie-Cités/CNRS, Paris}
    {Research Internship.}
    {\emph{Development of Accessim with Netlogo ABM platform.}}
  \entry
    {07–08 2006}
    {\href{http://www.aiec.fr}{Aiec.fr}}
    {Summer job.}
    {\emph{Development of an institutional website.}}
  \entry
    {06–09 2004}
    {Novaldi, Bayonne}
    {Professional Internship.}
    {\emph{Development of multiple institutional website.}}

\end{entrylist}

\section{educational}

\begin{entrylist}
  \entry
    {2011-2012}
    {Discussion Sections (TD)}
    {Md. of Geographic Information Systems Engineer}
    {Algorithmic and VBA programming language introduction, 40h}
  \entry
    {2010-2011}
    {Discussion Sections (TD)}
    {Md. of Geographic Information Systems Engineer}
    {VBA programming language introduction, 28h}
  \entry
    {2009-2010}
    {Discussion Sections (TD)}
    {Md. of Geographic Information Systems Engineer}
    {Management of VBA project, 12h}
\end{entrylist}

\section{scientific activities}

\begin{entrylist}
  \entry
    {June 2012}
    {MAPS-4 workshop}
    {http://maps.csregistry.org/home}
    {4th edition of the RNSC workshop MAPS (Multi Agent Modeling Applied to Spatialized Phenomena)}
  \entry
    {October 2011}
    {MAPS-3 workshop}
    {http://maps.csregistry.org/home}
    {3th edition of the RNSC workshop MAPS}
  \entry
    {since 2011}
    {Element'R workshop}
    {}
    {Multiple thematic workshops about R language and libraries}
  \entry
    {since 2011}
    {SimTools network}
    {http://sites.google.com/site/simtoolsnetwork/}
    {Creating innovating tools for complex system evaluation with other young computer scientists}
\end{entrylist}

\section{publications}
%\printbibsection{article}{article in peer-reviewed journal}
\printbibsection{inproceedings}{conferences and proceedings}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
